A Search for Supernova Remnants in NGC\,6946

### 2018-10-04 ms.tex
Updates from ShareLaTeX

\usepackage{natbib}
\usepackage{comment}
\begin{document}
%\slugcomment{Draft \today}

@@

Here we discuss a new, more sensitive optical search for SNRs in NGC6946 in which we identify a total of ?? SNR candidates using interference filters.  We also discuss spectroscopic observations of ?? of these candidates, which we use to verify  the ratios obtained from the imaging and to characterize our new optical sample.

@@

We used standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} techniques for processing the images, including overscan correction, bias subtraction, and flat-fielding using dome flats.  Procedures in the IRAF {\texttt mscred} package were then used to combine the data from the individual chips into a mosaic image for each frame, assigned a WCS for each using stars from the USNOB1 catalog, and then stacked  all the images by   filter onto an arbitrary standard coordinate system with a scale of 0\farcs 20 pixel$^{-1}$.  We then scaled and subtracted the continuum images from the emission-line ones (red from \ha\ and \sii; green from \oiii) to give pure emission-line images with most of the stars removed.  Finally, we used observations of several spectrophotometric standard stars from the catalog of \citet{massey88} to flux calibrate the emission-line images.  Figure 1 shows an RGB version of the final images (R = \ha, G = \sii, B = \oiii).

To select SNR candidates, we displayed continuum-subtracted WIYN images in all three emission lines, as well as \sii:\ha\  and \oiii:\ha\ ratio images, and a continuum image (to distinguish stars from nebulae), all in DS9.   We then visually inspected these to select SNR candidates based on a high  \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) conducted independent inspections, and then we conferred to agree on a consensus list of 146 candidates, including the 27 from MF97.   In addition, we selected 51 candidates with relatively high \oiii:\ha\ ratios, in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy.   Though none of these O-selected candidates had ratios as extreme as for Cas A or  1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  %while the GMOS was equipped with e2V CCD chips. (This is covered below-WPB) 
For the 2014A program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.
%For both programs we selected objects from the lists of SNR candidates in D10 and in a preliminary version of the catalog that later appeared in B12.
 %([based on our 2009 Magellan IMACS images) and D10, based on WFC3 images.  
 Slitlets in one or more of our eight masks were placed on ??? distinct SNR candidates, including ones with a range of sizes, galactocentric radii, and ISM environments (locations in arms and in 
 inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions  for comparison purposes in both 2014 and 2015.
 %\footnote{Exceptions are the very outermost regions of the galaxy, where the sparse population would have made less efficient use of the $5\farcm 5 \times 5\farcm 5$ GMOS field, and the innermost nuclear region, where source confusion and the high star density would have made sky subtraction difficult.}  
Figure \ref{fig.galaxy} shows all the objects from the {\bf [Need to revise this, make a figure, and get correct numbers]} B12, D10, and B14 catalogs, and highlights those for which we obtained spectra (red boxes).  %, and Table \ref{obs_log} lists all the SNR candidates for which we obtained spectra.

@@

\begin{figure}
\plotone{rgb_10arcmin_subtracted_2.png}
\caption{An emission-line image of \gal, after continuum subtraction, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left. }
\end{figure}

>>>>

\usepackage{natbib}
\usepackage{comment}
\usepackage{todonotes}
\begin{document}
%\slugcomment{Draft \today}

@@

Here we discuss a new, more sensitive optical search for SNRs in NGC6946 in which we identify a total of 147 SNR candidates using interference filters.  We also discuss spectroscopic observations of 102 of these candidates, which we use to verify  the ratios obtained from the imaging and to characterize our new optical sample.

@@

We used standard IRAF\footnote{IRAF is distributed by the National Optical Astronomy Observatory, which is operated by the Association of Universities for Research in Astronomy, Inc., under cooperative agreement with the National Science Foundation.} techniques for processing the images, including overscan correction, bias subtraction, and flat-fielding using dome flats.  Procedures in the IRAF {\texttt mscred} package were then used to combine the data from the individual chips into a mosaic image for each frame, assigned a WCS for each using stars from the USNOB1 catalog, and then stacked  all the images by   filter onto an arbitrary standard coordinate system with a scale of 0\farcs 20 pixel$^{-1}$.  We then scaled and subtracted the continuum images from the emission-line ones (red from \ha\ and \sii; green from \oiii) to give pure emission-line images with most of the stars removed.  Finally, we used observations of several spectrophotometric standard stars from the catalog of \citet{massey88} to flux calibrate the emission-line images.  Figure \ref{fig_overview} shows an RGB version of the final images (R = \ha, G = \sii, B = \oiii).

To select SNR candidates, we displayed continuum-subtracted WIYN images in all three emission lines, as well as \sii:\ha\  and \oiii:\ha\ ratio images, and a continuum image (to distinguish stars from nebulae), all in DS9.   We then visually inspected these to select SNR candidates based on a high  \sii:\ha\ ratio.  The initial inspection was carried out by Middlebury undergraduate Marc DeLaney; subsequently two of us (WPB and PFW) conducted independent inspections, and then we conferred to agree on a consensus list of 147 candidates, including the 27 from MF97.   In addition, we selected 51 candidates with relatively high \oiii:\ha\ ratios, in an attempt to identify young, ejecta-dominated SNRs such as Cas A in the Galaxy.   Though none of these O-selected candidates had ratios as extreme as for Cas A or  1E0102-72.3 in the Small Magellanic Cloud, we nevertheless selected some of these for follow-up spectroscopy.

@@

We used the Gemini Multi-Object Spectrograph (GMOS) on the 8.2m Gemini-North telescope to obtain all the spectra reported here, during queue-scheduled programs in semesters 2014B (program GN-2014B-Q-83) and 2015B (program GN-2015B-Q-91).  %while the GMOS was equipped with e2V CCD chips. (This is covered below-WPB) 
For the 2014A program, we designed six custom masks, each with 20-30 slitlets targeting SNR candidates whose positions we determined from our 2011 WIYN images, together with  short $R$-band pre-images of several \gal\ fields taken with GMOS earlier in 2014 as part of the spectroscopy program.    
We used two additional masks (which we refer to as masks 7 and 8 for simplicity)  for the 2015B program.
%For both programs we selected objects from the lists of SNR candidates in D10 and in a preliminary version of the catalog that later appeared in B12.
 %([based on our 2009 Magellan IMACS images) and D10, based on WFC3 images.  
 Slitlets in one or more of our eight masks were placed on 102 distinct SNR candidates, including ones with a range of sizes, galactocentric radii, and ISM environments (locations in arms and in 
 inter-arm regions).  In addition to the SNR candidates, we also placed a number of slitlets on prominent \hii\ regions  for comparison purposes in both 2014 and 2015.
 %\footnote{Exceptions are the very outermost regions of the galaxy, where the sparse population would have made less efficient use of the $5\farcm 5 \times 5\farcm 5$ GMOS field, and the innermost nuclear region, where source confusion and the high star density would have made sky subtraction difficult.}  
Figure \ref{fig_overview} shows all the objects from the sample for for which we obtained spectra (red boxes).  %, and Table \ref{obs_log} lists all the SNR candidates for which we obtained spectra.

\todo[inline]{This figure needs to be redone with the SNRs for which we obtained spectra indicated.}

@@

\begin{figure}
\plotone{rgb_10arcmin_subtracted_2.png}
\caption{An emission-line image of \gal, after continuum subtraction, where R = \ha, G = \sii, and B = \oiii.  The field is 10\arcmin\ square and is oriented N up, E left. \label{fig_overview} }
\end{figure}
